---
title: "p8105_hw3_sl5009"
author: "Shengzhi Luo"
date: "15/10/2021"
output: github_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```

## Problem 1

```{r}
library(p8105.datasets)
data("instacart")
```

```{r,message=FALSE}
library(tidyverse)
library(dplyr)

knitr::opts_chunk$set(
  fig.width = 6,
  fig.asp = .6,
  out.width = "90%"
)

theme_set(theme_minimal() + theme(legend.position = "bottom"))

options(
  ggplot2.continuous.colour = "viridis",
  ggplot2.continuous.fill = "viridis"
)

scale_colour_discrete = scale_colour_viridis_d
scale_fill_discrete = scale_fill_viridis_d
```
How many aisles are there, and which aisles are the most items ordered from?

```{r}
instacart %>%
  group_by(aisle,aisle_id) %>% 
  summarise(n_obs=n()) %>% 
  arrange(desc(n_obs))
```
As from the above table, we can see there are 134 aisles in total and the most items ordered are fresh vegetables.


```{r}
instacart %>%
  group_by(aisle,aisle_id) %>% 
  summarise(n_obs=n()) %>% 
  filter(n_obs>10000) %>% 
  ggplot(aes(x = aisle_id, y = n_obs, color = aisle_id)) + 
    geom_point() + geom_line() + 
    theme(legend.position = "bottom")
```
Make a table showing the three most popular items in each of the aisles “baking ingredients”, “dog food care”, and “packaged vegetables fruits”. Include the number of times each item is ordered in your table.
```{r,include=FALSE}
```
Make a table showing the mean hour of the day at which Pink Lady Apples and Coffee Ice Cream are ordered on each day of the week; format this table for human readers (i.e. produce a 2 x 7 table).

```{r}
instacart %>% 
  filter(product_name==c("Pink Lady Apples","Coffee Ice Cream")) %>% 
  select(order_dow,order_hour_of_day,product_name) %>% 
  group_by(order_dow,product_name) %>% 
  summarise(mean_hour=mean(order_hour_of_day)) %>% 
  pivot_wider(
    names_from = order_dow, 
    values_from = mean_hour
  )
```


