---
title: "p8105_hw3_sl5009"
author: "Shengzhi Luo"
date: "15/10/2021"
output: github_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```

## Problem 1

```{r}
library(p8105.datasets)
data("instacart")
```

Description of the dataset:
There are 15 variables with 1384617 columns showing the online grocery orders from 131,209 unique users, where each row in the dataset is a product from an order. Order_dow is the day of the week on which the order was placed with 0 meaning Monday and so on. Aisle_id is aisle identifier. Days_since_prior_order is days since the last order, capped at 30, NA if order_number=1.

```{r,message=FALSE}
library(tidyverse)
library(dplyr)

knitr::opts_chunk$set(
  fig.width = 15,
  fig.asp = .8,
  out.width = "150%"
)

theme_set(theme_minimal() + theme(legend.position = "bottom"))

options(
  ggplot2.continuous.colour = "viridis",
  ggplot2.continuous.fill = "viridis"
)

scale_colour_discrete = scale_colour_viridis_d
scale_fill_discrete = scale_fill_viridis_d
```
### Part 1 

```{r}
instacart %>%
  group_by(aisle,aisle_id) %>% 
  summarise(n_obs=n()) %>% 
  arrange(desc(n_obs))
```
As from the above table, we can see there are 134 aisles in total and the most items ordered are fresh vegetables.

### Part 2

```{r}
instacart %>%
  group_by(aisle,aisle_id) %>% 
  summarise(n_obs=n()) %>% 
  filter(n_obs>10000) %>% 
  ggplot(aes(x = aisle_id, y = n_obs, color = aisle_id)) +
    geom_point() + geom_line() +
    theme(legend.position = "bottom")
```
Fresh fruits and fresh vegetables are most frequently ordered among all groceries. Reasons may be fresh food have short expiration so that people have to buy them more often. 

### Part 3

```{r}
instacart %>% 
  filter(aisle==c("baking ingredients","dog food care","packaged vegetables fruits")) %>% 
  group_by(aisle) %>% 
  count(product_name,name = "product_count") %>% 
  mutate(product_rank=min_rank(desc(product_count))) %>% 
  filter(product_rank<=3) %>% 
  arrange(aisle,product_rank) %>% 
  knitr::kable()
```

The most poppular three things ordered in baking ingredients are Light Brown Sugar, Pure Baking Soda and Organic Vanilla Extract with 157, 149 and 122 times ordered for each. 
The most poppular three things ordered in dog food care are Organix Grain Free Chicken & Vegetable Dog Food, Organix Chicken & Brown Rice Recipe and Original Dry Dog with 14, 13 and 9 times ordered for each. 
The most poppular three things ordered in packaged vegetables fruits are Organic Baby Spinach, Organic Raspberries and Organic Blueberries with 3324, 1920, 1692 times ordered for each.
Organic food is very popular among groceries. 

### Part 4

```{r,message=FALSE}
mean_instacart =
  instacart %>% 
  filter(product_name==c("Pink Lady Apples","Coffee Ice Cream")) %>% 
  select(order_dow,order_hour_of_day,product_name) %>% 
  group_by(order_dow,product_name) %>% 
  summarise(mean_hour=mean(order_hour_of_day)) %>% 
  pivot_wider(
    names_from = order_dow, 
    values_from = mean_hour
  ) 
colnames(mean_instacart)<-c("product_name","Monday","Tuesday","Wednesday","Thursday","Friday","Saturday","Sunday")
mean_instacart=knitr::kable(mean_instacart,digits = 1)
mean_instacart

```

These two drinks are evenly ordered through all week. Coffee Ice Cream is slightly more popular than Pink Lady Apples.


## Problem 2

```{r}
library(p8105.datasets)
data("brfss_smart2010")
brfss_smart2010=janitor::clean_names(brfss_smart2010)
```

### Data Cleaning

```{r}
brfss_smart2010_OH=
  brfss_smart2010 %>% 
  filter(topic=="Overall Health") %>% 
  mutate(response = forcats::fct_relevel(response, c("Poor","Fair","Good","Very good","Excellent"))) %>%
  arrange(year,locationabbr,response)
brfss_smart2010_OH
```

### Part 1


```{r}
brfss_smart2010_OH %>% 
  filter(year=="2002") %>% 
  group_by(locationabbr) %>% 
  distinct(locationdesc) %>% 
  summarise(location_obs=n()) %>% 
  filter(location_obs>=7) %>% 
  knitr::kable()
brfss_smart2010_OH %>% 
  filter(year=="2010") %>% 
  group_by(locationabbr) %>% 
  distinct(locationdesc) %>% 
  summarise(location_obs=n()) %>% 
  filter(location_obs>=7) %>% 
  knitr::kable()
```
Connecticut, Florida, Massachusetts, North Carolina, New Jersey, Pennsylvania are observed at least 7 locations in 2002. California, Colorado, Florida, Massachusetts, Maryland, North Carolina, Nebraska, New Jersey, New York, Ohio, Pennsylvania, South Carolina, Texas, Washington are observed at least 7 locations in 2010.

### Part 2

```{r}
brfss_smart2010_OH_mean=
  brfss_smart2010_OH %>% 
  filter(response=="Excellent") %>% 
  group_by(year,locationabbr) %>% 
  summarise(
    mean_data=mean(data_value)
  ) %>% 
  mutate(
    mean_data=round(mean_data,digits = 2)
  )
brfss_smart2010_OH_mean
brfss_smart2010_OH_mean %>% 
  ggplot(aes(x = locationabbr, y = mean_data, color = year)) + 
    geom_point() + geom_line() + 
    theme(legend.position = "bottom")
```
According the plot above, The response values within nearly every state declined from year 2002 to 2010.

### Part 3

```{r}
brfss_smart2010_OH %>% 
  filter(locationabbr=="NY",year==c("2006","2010")) %>% 
  ggplot(aes(x =data_value, fill = response)) +
  geom_density(alpha = .5) + 
  facet_grid(~year) + 
  viridis::scale_fill_viridis(discrete = TRUE)
```

In 2002, responses as Poor in NY are more common than these in 2010.
Responses to very good in both 2002 and 2010 have more values than others.

## Problem 3

### Part 1

```{r}
accel_data=
  read.csv("accel_data.csv") %>% 
  mutate_if(is.numeric, round, 1) %>%
  mutate(weekday_or_weekend=ifelse(day %in% c("Saturday", "Sunday"), "weekend", "weekday")) %>% 
  relocate(weekday_or_weekend,.after = day) %>% 
  pivot_longer(
    activity.1:activity.1440,
    names_to = "over_a_day", 
    names_prefix = "activity.",
    values_to = "activity"
  ) 
accel_data
```
We group the data by day and pivot the activity through 24 hours. There are 6 variables with 50400 obsevations. over_a_day variable refers to the ith minute 
of the day and activity refers to the activity observed for every minute.

### Part 2

```{r}
sum_of_day=
  accel_data %>% 
  group_by(day_id) %>% 
  summarise(total_activity=sum(activity)) %>% 
  arrange(desc(total_activity)) %>% 
  knitr::kable()
sum_of_day
```
The 16th and 4th day of 35 days have the most total activity values. But this table can't show any trends apparently since there isn't any 24-hour activity changes.

```{r}
accel_data_24h=
  accel_data %>% 
  group_by(day_id) %>% 
  ggplot(aes(x =over_a_day, y =activity, color = day)) + 
    geom_point() + geom_line() + 
    theme(legend.position = "bottom")
accel_data_24h
```
According to this plot, morning and evening activities in the day are more efficient. 
Activities in Friday mornings and Sunday evenings are often more active than others. 

